On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-26 Manuscript/manuscript.tex
Update, still need to make format changes

\jy{Are the results from exponential margins the same? If so, we can put them in
  an appendix; make sure we have the data generation process accurately
  described. Then briefly summarize and refer to it at the end of the simulation
  section.}

\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
  would show a lot of diff while there is no diff.}

@@

\jy{Could do one for the exponential margin study too. Maybe for the negative dependence.}

@@

\jy{Motivation; data generation (calibration of copula parameters to give the
  desired rho); simulation design; plots; brief discussion of results.}

This appendix concerns the performance of block bootstrap when used to estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
AR(1) process with an underlying exponential marginal distribution. The 
motivation for this additional simulation study was to observe if the results of 
the main simulation study will change if the underlying marginal distribution is
not normal. The data

>>>>

\jy{Are the results from exponential margins the same? If so, we can put them in
  an appendix; make sure we have the data generation process accurately
  described. Then briefly summarize and refer to it at the end of the simulation
  section.} \mc{addressed}

\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
  would show a lot of diff while there is no diff.}
\mc{addressed}

@@

\jy{Could do one for the exponential margin study too. 
Maybe for the negative dependence.}
\mc{created negative dependence plots not included in manuscript yet}

@@

\jy{Motivation; data generation (calibration of copula parameters to give the
  desired rho); simulation design; plots; brief discussion of results.}
\mc{addressed}

This appendix concerns the performance of block bootstrap when used to estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
AR(1) process with an underlying exponential marginal distribution. The 
motivation for this additional simulation study was to observe if the results of 
the main simulation study will change if the underlying marginal distribution is
not normal.

We generated time series $X_t$ from a 1st order autoregressive 
(AR(1)) process as we did previously, but transformed the data from a standard
normal distribution to an exponential distribution with rate $\lambda = 1$, so 
that for $t \in \{1, \ldots, n\}$, we can define:
\begin{equation}
W_t = F^{-1}(\Phi(X_t), 1)
\end{equation}
where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
distribution with rate parameter $\lambda$.

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
Although we may have set $\phi$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five autocorrelation coefficients for $W_t$ will be different.
\mc{I may need some help explaining the calibration of copula parameters}
After calibrating the copula parameters, we can again plot empirical coverage 
rates and the 95\% confidence intervals of the real coverage.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of an AR(1) process with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of an AR(1) process with AR 
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_rho}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\rho$ of an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi}
\end{figure}

Additionally, another set of 50 CIs was generated for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/exp_rho_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$ 
    transformed to an exponential distribution iwth $\lambda = 1$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:eri}
\end{figure}

Although there are differences in the ranges of sample sizes needed to cover 
parameters of a normally distributed AR(1) process versus an exponentially 
distributed AR(1) process, the trends and patterns are generally the same.
Student's $t$ CIs still appear to yield higher coverage rates than other 
methods. Performance is still generally better when temporal dependence is 
negative rather than positive. Most importantly, percentile, BC, and BCA CIs
still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
in \textbf{Figure~\ref{fig:eri}}, percentile and BC CIs still have the same bias
issue.
